Extrinsic Calibration of 2D Laser Range Finders \\ using Planar Features

### 2019-03-28 paper.tex
removed hyperref to pass ieee standards

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{hyperref}
\usepackage[noabbrev, capitalize]{cleveref}
\usepackage{bm}
\usepackage{tabu}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{bookmark}
\usepackage{dsfont}

@@

@@

@@

This calibration is utterly necessary because any error introduces a shift on the position of each point, which in turn can be seen as deformations on the point cloud resulting from the acquisition. Such deformation can be seen in \cref{fig:deformed-pointcloud}, which is shown as multiple misalign planes. These deformations have a significant impact on subsequent point cloud processing methods, that rely on the accurate representation of the 3D environments, i.e. registration (for example, ICP), segmentation and feature extraction algorithms.

@@

The hardware infrastructure used in this work to acquire the data was the 3D scanner \textit{lemonbot}, show in \cref{figure:lemonbot}. The principal components of this 3D scanner are the PTU \textit{FLIR PTU-D46} and the 2D laser scanner \textit{Hokuyo UTM30LX}\footnote{The 3D scanner, as seen in the \cref{figure:lemonbot}, has two laser scanners: the \textit{Hokuyo UTM30LX} and the \textit{SICK LMS100}. In this work, only the first was used.}. The LRF was mounted on the PTU, to have the scan plane in the vertical direction. The laser scanner can cover \SI{270}{\degree} with an angular resolution of \SI{0.25}{\degree}. The PTU has an angular resolution of \SI{0.0032}{\degree}, so the error in the transformation $^{m}\mathbf{T}_{e}$ (see \cref{equation:point-reconstruction}) is negligible. This 3D scanner was programmed using the \textit{ROS} framework, which handles the hardware drivers, the transformation graph and the recording of the scanning data.

@@

The optimization procedure was successful minimizing the objective function in every dataset, as seen in \cref{table:iteration-results}. The final results in a qualitative improvement in comparison to the uncalibrated point cloud, as shown in \cref{figure:visual-comparison}. These examples show the most common defects shown in poorly calibrated reconstructions. In the first example, the roof surface appears as multiple unaligned surfaces. This effect can be also seen in a wall, in the third example, which appears in duplication. The second example shows a deformation, which evidently deformed the corner structure in the point cloud. These deformations found in the uncalibrated point clouds are almost imperceptible in the calibrated point cloud.

@@

This method was performed for 3 manually segmented planes, such as the ones seen in \cref{figure:cluster-segmentation-1}, and the segments can be seen in \cref{table:quantitative-results}. As seen the statistical deviation is, in fact, smaller in the calibrated point cloud. As an alternative view, in \cref{figure:deviation-histogram}, the histogram, and distribution of the signed deviation are shown for both the point clouds. As shown, the deviations of the calibrated point cloud are less scattered than the deviations of the uncalibrated point cloud. These results indicate that this calibration method, in fact, improves the results.

@@

Further work can be done in order to improve or validate further this algorithm, such as: a study of a automatic segmentation procedure; the determination of the Jacobian of the cost function, in order to reduce the iteration time of the optimization, by enabling new optimization methods, such as the gradient descent; the validation of this method with data using different 2D-LRF and different dynamic kinematic chains, such as a robotic arm; the comparison of the point cloud generated with this reconstruction method with point clouds generated with high-end commercial 3D scanners, such as the \textit{FARO Focus 3D}; and study the impact of the calibration environment (for example, the number and pose of the planes and size of the room) in the calibration accuracy.

>>>>

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{siunitx}
\usepackage{url}
\usepackage{bm}
\usepackage{tabu}
\usepackage{booktabs}
\usepackage{subfig}
\usepackage{dsfont}

@@

\IEEEoverridecommandlockouts
\IEEEpubid{\makebox[\columnwidth]{978-1-7281-3558-8/19/\$31.00~\copyright2019 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

@@

\IEEEpubidadjcol

@@

This calibration is utterly necessary because any error introduces a shift on the position of each point, which in turn can be seen as deformations on the point cloud resulting from the acquisition. Such deformation can be seen in Figure \ref{fig:deformed-pointcloud}, which is shown as multiple misalign planes. These deformations have a significant impact on subsequent point cloud processing methods, that rely on the accurate representation of the 3D environments, i.e. registration (for example, ICP), segmentation and feature extraction algorithms.

@@

The hardware infrastructure used in this work to acquire the data was the 3D scanner \textit{lemonbot}, shown in Figure \ref{figure:lemonbot}. The principal components of this 3D scanner are the PTU \textit{FLIR PTU-D46} and the 2D laser scanner \textit{Hokuyo UTM30LX}\footnote{The 3D scanner, as seen in the Figure \ref{figure:lemonbot}, has two laser scanners: the \textit{Hokuyo UTM30LX} and the \textit{SICK LMS100}. In this work, only the first was used.}. The LRF was mounted on the PTU, to have the scan plane in the vertical direction. The laser scanner can cover \SI{270}{\degree} with an angular resolution of \SI{0.25}{\degree}. The PTU has an angular resolution of \SI{0.0032}{\degree}, so the error in the transformation $^{m}\mathbf{T}_{e}$ (see Equation \ref{equation:point-reconstruction}) is negligible. This 3D scanner was programmed using the \textit{ROS} framework, which handles the hardware drivers, the transformation graph and the recording of the scanning data.

@@

The optimization procedure was successful minimizing the objective function in every dataset, as seen in Table \ref{table:iteration-results}. The final results in a qualitative improvement in comparison to the uncalibrated point cloud, as shown in Figure \ref{figure:visual-comparison}. These examples show the most common defects shown in poorly calibrated reconstructions. In the first example, the roof surface appears as multiple unaligned surfaces. This effect can be also seen in a wall, in the third example, which appears in duplication. The second example shows a deformation, which evidently deformed the corner structure in the point cloud. These deformations found in the uncalibrated point clouds are almost imperceptible in the calibrated point cloud.

@@

This method was performed for 3 manually segmented planes, such as the ones seen in Figure \ref{figure:cluster-segmentation-1} and the segments can be seen in Table \ref{table:quantitative-results}. As seen the statistical deviation is, in fact, smaller in the calibrated point cloud. As an alternative view, in Figure \ref{figure:deviation-histogram}, the histogram, and distribution of the signed deviation are shown for both the point clouds. As shown, the deviations of the calibrated point cloud are less scattered than the deviations of the uncalibrated point cloud. These results indicate that this calibration method, in fact, improves the results.

@@

Future work can be done in order to improve or validate further this algorithm, such as a study of an automatic segmentation procedure; the determination of the Jacobian of the cost function, in order to reduce the iteration time of the optimization, by enabling new optimization methods, such as the gradient descent; the validation of this method with data using different 2D-LRF and different dynamic kinematic chains, such as a robotic arm; the comparison of the point cloud generated with this reconstruction method with point clouds generated with high-end commercial 3D scanners, such as the \textit{FARO Focus 3D}; and study the impact of the calibration environment (for example, the number and pose of the planes and size of the room) in the calibration accuracy.
